Integer Programming on Ising Spin-Glass

### 2020-09-14 paper/main.tex
Added funding infos
Fixed reference issue for penalty resolution

The integer linear optimization problem is then solved through the minimization of the quadratic objective function
\begin{align}
 \chi^2(\vec \Psi)
 &=
 \vec c^T T_x \vec \Psi_x + p \left\| A T_s \vec \Psi_x + T_s \vec \Psi_s + \vec b \right\|^2
\end{align}
where $p$ is an external parameter representing the strength of the penalty when violating constraints.
This parameter needs to be sufficiently large, e.g., $p \geq \vec c \cdot \vec x$, to ensure the constraints are indeed fulfilled\footnote{Depending on the problem, $p$ can be smaller as well.
For example, in the case of the MDS, $p\geq 1$ suffices.}.
The objective function $\chi^2$ can be represented as a QUBO Hamiltonian
\begin{align}
 \chi^2(\vec \Psi) =    &
 \vec \Psi^T
 \begin{pmatrix}
  Q_{xx} & Q_{xs} \\
  Q_{sx} & Q_{ss}
 \end{pmatrix}
 \vec \Psi + p\left \| \vec b \right\|^2, \\
 \equiv &  \vec \Psi^T Q  \vec \Psi + C,
 \label{eq:matrix_form}
\end{align}
where
{\small
\begin{align}
 \label{eq:qubo:components}
 Q_{xx} = & p {T_{x}}^T \left[ A^T A + \mathrm{diag} \left(A^T \vec b + \vec b^T A\right) \right] T_x + \mathrm{diag}(\vec c) T_x,                                                                    \\
 Q_{xs} = & Q_{sx}^T = p {T_{x}}^T A^T T_s,                                                                     \\
 Q_{ss} = & p\left[ {T_{s}}^T T_s + \mathrm{diag}\left( {T_{s}}^T \vec b + \vec b^T T_s\right) \right].
\end{align}}
The function $\mathrm{diag}(\vec v)$ transforms a vector $\vec v$ into a diagonal matrix, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.

@@

The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:qubo-min} {\color{red}@chris what equation is this?} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
Thus some knowledge of the problem is required.
In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values of For$p$ increase the highest available energy of the system by multiples of $p$.
After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.

@@

We thank Long Gang Pang for initial discussions.
We thank David Johnson, Vlad Papish and the rest of D-Wave Support for answering detailed questions about the D-Wave annealer.

@@

Initial idea was proposed by Chang.
All authors contributed to the design of test cases.
Calculations were performed on the D-Wave by Chang and K\"oerber.
Numerical simulations were performed by Chen, Chang, and K\"orber.
All authors contributed to writing and editing of the final manuscript.

>>>>

The integer linear optimization problem is then solved through the minimization of the quadratic objective function
\begin{align}
 \label{eq:ilp-slack-bit-energy}
 \chi^2(\vec \Psi)
 &=
 \vec c^T T_x \vec \Psi_x + p \left\| A T_s \vec \Psi_x + T_s \vec \Psi_s + \vec b \right\|^2
\end{align}
where $p$ is an external parameter representing the strength of the penalty when violating constraints.
This parameter needs to be sufficiently large, e.g., $p \geq \vec c \cdot \vec x$, to ensure the constraints are indeed fulfilled\footnote{Depending on the problem, $p$ can be smaller as well.
For example, in the case of the MDS, $p\geq 1$ suffices.}.
The objective function $\chi^2$ can be represented as a QUBO Hamiltonian
\begin{align}
 \chi^2(\vec \Psi) =    &
 \vec \Psi^T
 \begin{pmatrix}
  Q_{xx} & Q_{xs} \\
  Q_{sx} & Q_{ss}
 \end{pmatrix}
 \vec \Psi + p\left \| \vec b \right\|^2, \\
 \equiv &  \vec \Psi^T Q  \vec \Psi + C,
 \label{eq:matrix_form}
\end{align}
where
{\small
\begin{align}
 \label{eq:qubo:components}
 Q_{xx} = & p {T_{x}}^T \left[ A^T A + \mathrm{diag} \left(A^T \vec b + \vec b^T A\right) \right] T_x + \mathrm{diag}(\vec c) T_x,                                                                    \\
 Q_{xs} = & Q_{sx}^T = p {T_{x}}^T A^T T_s,                                                                     \\
 Q_{ss} = & p\left[ {T_{s}}^T T_s + \mathrm{diag}\left( {T_{s}}^T \vec b + \vec b^T T_s\right) \right].
\end{align}}
The function $\mathrm{diag}(\vec v)$ transforms a vector $\vec v$ into a diagonal matrix, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.

@@

The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
Thus some knowledge of the problem is required.
In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values of For $p$ increase the highest available energy of the system by multiples of $p$.
After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.

@@

We thank Long Gang Pang for initial discussions.
We thank David Johnson, Vlad Papish and the rest of D-Wave Support for answering detailed questions about the D-Wave annealer.
C.K. gratefully acknowledges funding through the Alexander von Humboldt Foundation through a Feodor Lynen Research Fellowship.

@@

Initial idea was proposed by Chang.
All authors contributed to the design of test cases.
Calculations were performed on the D-Wave by Chang and K\"orber.
Numerical simulations were performed by Chen, Chang, and K\"orber.
All authors contributed to writing and editing of the final manuscript.
